Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Fixes on AA comments

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  
\red{[what does it mean that it is continuous ``at the sample times''? We're working in frequency. Are you matching poles? There is still no clear relationship between continuous and samples transfer functions, it is not formal in my opinion.]}
This pulse transfer function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

\begin{myassumption}
%
The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
sampling the plant output at ADC and updating the DAC accordingly.
%
\end{myassumption}

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ \red{[is this a new notation over the time domain? It does not reflect the signals used in the plot -- utterly confusing!]} at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$.
%
\end{myassumption}

\begin{myassumption}
%
\label{assumption:cont_and_plant}
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, 
\red{[!! of course, we're working with transfer functions!!]}
any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded \red{[how is this related to ADC/DAC? very confusing.]}
. Additionally, the pulse transfer function is obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$. \red{[clarify this: this cannot be an assumption, since it is hinging on a specific numerical scheme. Assumptions deal with structural properties for example, or choices of certain parameters ... ]}
%
\end{myassumption}

Although the pulse transfer function $G(z)$ represents adequately \red{[clarify adverb]} $G(s)$ in the z-domain, 
the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. 
These uncertainties may be \red{[clarify use of conditional tense]} parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be \red{[\ldots]} represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}
\red{[same order?]}

@@

A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

>>>>

\begin{myassumption}
%
The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
%
\end{myassumption}

\begin{mylemma}\cite{astrom1997computer}
%
Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula: 
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{ie} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
\red{[same order?]}

@@

A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G_p(s)$}};
   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };
